Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions

### 2008-10-26 lda-paper.tex
research & paper change!

Extractors:
\begin{itemize}
\item CVSSuck - CVS Suck mirrors RCS files from a CVS repository. 
\item softChange - extract CVS facts to a PostgreSQL database.
\item bt2csv - Convert BitKeeper repositories to facts in CSV
  databases.
\end{itemize}

Analysis Tools:
\begin{itemize}
\item Hiraldo-Grok - An OCaml based spin off of Grok used for
  answering queries.
\item Gnuplot - graph plotting package
\end{itemize}

>>>>

To extract data from CVS and BitKeeper we used softChange to extract
CVS repositories and provide a schema for our revision data. We used
bt2csv to extract BitKeeper revisions from BitKeeper web repositories.

% Extractors:
% \begin{itemize}
% \item CVSSuck - CVS Suck mirrors RCS files from a CVS repository. 
% \item softChange - extract CVS facts to a PostgreSQL database.
% \item bt2csv - Convert BitKeeper repositories to facts in CSV
%   databases.
% \end{itemize}

Our analysis tools consisted of: Hiraldo-Grok, an OCaml based spin off
of Grok used for answering queries; Gnuplot, a graph plotting package,
lda-c a LDA package by Biel
